Plot previous findings

### 2024-11-04 code_data/previous_studies/PreviousFindings.Rmd
Updated via the Open Science Framework

RT_plot <- ggplot(data=filter(estimates, region %in% c("pre-critical", "critical", "spill-over")),
                       aes(x=int_type, y=mean, ymin=lower, ymax=upper )) +
                  geom_pointrange(aes(color=experiment, shape=measure), 
                       size=0.8, position=position_dodge(1.45))+
                  scale_shape_manual(values = c(18,16,17,15), breaks=c("SPR", "FPRT", "RPD", "TFT"),
                                     labels=c("self-paced reading time", "first-pass reading time", "regression path duration", "total fixation time"))+
                  scale_color_manual(values = c(my_colors[3], my_colors[4],my_colors[5],my_colors[8],my_colors[9], "black"))+
                  geom_hline(yintercept=0, linetype="solid", alpha=.5)+
                  facet_grid(region~int_type, scales="free", space="free") +
                  theme_bw(base_size = 15)+
                  scale_x_discrete(breaks = NULL)+
                  theme(legend.position="right", legend.box="vertical", legend.direction="vertical")+
                  xlab("")+
                  ylab("reading time difference (ms)")+
                  #ggtitle("Present and previous findings")+
                  guides(shape = guide_legend(order = 2),col = guide_legend(order = 1))+
                  coord_cartesian(ylim=c(-75, 150)) +
                  ggtitle("Reading time differences") 
ggsave("plots/present_previous_findings.jpg", width=9, height=8, dpi=600)

@@

load("BFs_schoknecht.Rda")
df.bf_schoknecht$Experiment <- "present"

>>>>

RT_plot <- ggplot(data=filter(estimates, region %in% c("pre-critical", "critical", "spill-over")),
                       aes(x=int_type, y=mean, ymin=lower, ymax=upper )) +
                  geom_pointrange(aes(color=experiment, shape=measure), 
                       size=0.8, position=position_dodge(1.45))+
                  scale_shape_manual(values = c(18,16,17,15), breaks=c("SPR", "FPRT", "RPD", "TFT"),
                                     labels=c("self-paced reading time", "first-pass reading time", "regression path duration", "total fixation time"))+
                  scale_color_manual(values = c(my_colors[3], my_colors[4],my_colors[5],my_colors[8],my_colors[9], "black"))+
                  geom_hline(yintercept=0, linetype="solid", alpha=.5)+
                  facet_grid(region~int_type, scales="free", space="free") +
                  theme_bw(base_size = 15)+
                  scale_x_discrete(breaks = NULL)+
                  theme(legend.position="right", legend.box="vertical", legend.direction="vertical")+
                  xlab("")+
                  ylab("reading time difference (ms)")+
                  #ggtitle("Present and previous findings")+
                  guides(shape = guide_legend(order = 2),col = guide_legend(order = 1))+
                  coord_cartesian(ylim=c(-75, 250)) +
                  ggtitle("Reading time differences") 
ggsave("plots/present_previous_findings.jpg", width=9, height=8, dpi=600)

@@

load("../SPR/r_scripts/BFs_schoknecht.Rda")
df.bf_schoknecht$Experiment <- "present"
